\begin{resume_section}{Qualifications and Skills}
	\textbf{Programming} \> C, C++, Java, Python, Bash, Batch File, \LaTeX \\
	\textbf{Certifications} \> Microsoft (Office 2016) Excel + Word + PowerPoint + IC3 GS5 Key Applications; MTA: Windows® Operating System Fundamentals \\
	\textbf{Languages} \> Fluent in English; Conversational in Mandarin \& Cantonese; Basic Proficiency in Spanish
\end{resume_section}

\medskip

\begin{resume_section}{Academics and Education}
	\textbf{Cypress Bay High School} \hspace*{\fill} \textsc{August 2020 -- Present}

	\smallskip

	\textsc{Relevant Coursework}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Advanced Placement (AP) -- Computer Science A/Principles, Physics C: Mechanics, Physics C: Electricity \& Magnetism, Physics 1, Calculus AB/BC
		\item Computer and Network Security Fundamentals, Operational Cyber Security and Essentials
	\end{itemize}
\end{resume_section}

\medskip

\begin{resume_section}{Extracurricular Activities}
	\textbf{Cybersecurity Club} \hspace*{\fill} \textsc{Fall 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Vice President of Competitions; VP of Training -- Managed the competition aspect of the club; Delivered weekly lectures at club meetings.
	\end{itemize}

	\textbf{Robotics Club} \hspace*{\fill} \textsc{Fall 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Community Service Officer -- Coordinated community service events throughout the year.
	\end{itemize}

	\textbf{Bilancio Robotics} \hspace*{\fill} \textsc{Fall 2022 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Chief Executive Officer -- Led a MATE ROV team in an underwater robotics competition.
	\end{itemize}

	\textbf{Computer Science Honor Society} \hspace*{\fill} \textsc{Fall 2021 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Tutoring Head -- Held weekly tutoring sessions for students in computer science.
	\end{itemize}

	\textbf{Mu Alpha Theta} \hspace*{\fill} \textsc{Fall 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Member (Competitor) -- Competed in various competitions monthly, and tutored peers. 
	\end{itemize}
\end{resume_section}

\medskip

\begin{resume_section}{Community Service}
	\textbf{Motorola’s “Take Your Child to Work Day”} \hspace*{\fill} \textsc{Summer 2022 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Demonstrated competition robots at a Motorola event for the participating students/children at the start of every summer.
	\end{itemize}

	\textbf{Weston Branch Library} \hspace*{\fill} \textsc{Summer 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Increased the accessibility of my local library since the COVID-19 pandemic by annotating books for students to read.
	\end{itemize}

	\textbf{STEM Tutoring} \hspace*{\fill} \textsc{Fall 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Mentored students after school in computer science and mathematics, specifically.
	\end{itemize}

	\textbf{Computer/Laptop Technician} \hspace*{\fill} \textsc{Fall 2021}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Helped set up computers/laptops at a local middle school for its students and staff before the beginning of a school year.
	\end{itemize}
\end{resume_section}

\medskip

\begin{resume_section}{Awards and Honors}
	\textbf{United States of America Computing Olympiad} \hspace*{\fill} \textsc{Winter 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Competitor in USACO’s Silver Division.
	\end{itemize}

	\textbf{TryHackMe's King of The Hill} \hspace*{\fill} \textsc{Fall 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Former USA National Champion in TryHackMe’s competitive hacking leaderboard.
	\end{itemize}

	\textbf{MIT's Battlecode} \hspace*{\fill} \textsc{Winter 2020 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Held a Top 10 Rating (2023 High School Division) in MIT’s Premier Programming Competition
	\end{itemize}

	\textbf{National Cyber Scholarship Finalist} \hspace*{\fill} \textsc{Fall 2021 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Received the Gold award in CyberStart America 2022.
	\end{itemize}

	\textbf{FIRST Tech Challenge (FTC)} \hspace*{\fill} \textsc{Fall 2021 -- Present}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Florida’s FTC 2022 Robotics State Championship - Connect Award 1st Place
		\item South Florida’s FTC 2022 Robotics League Tournament - Inspire Award 1st Place
	\end{itemize}

	\textbf{SkillsUSA (Cyber Security)} \hspace*{\fill} \textsc{Winter 2022 -- Spring 2023}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item 2nd Place Silver Medalist in Florida’s 2023 Cyber Security State Conference
		\item 1st Place Gold Medalist (2023 Regionals)
	\end{itemize}
\end{resume_section}

\medskip

\begin{resume_section}{Work Experience}
	\textbf{Mathnasium} \hspace*{\fill} \textsc{Summer 2022}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Worked as a student instructor and mentored students in various levels of mathematics, many hours a week.
	\end{itemize}

	\textbf{Motorola Solutions Shadowing} \hspace*{\fill} \textsc{Summer 2023}

	\begin{itemize}
		\setlength{\labelsep}{0.1in}
		\item Shadowed and worked with electrical and software engineers at a Motorola Solutions facility.
	\end{itemize}
\end{resume_section}
